% !TeX spellcheck = en_US
\documentclass[10pt, letterpaper, sans]{moderncv}

\moderncvstyle{banking}

\moderncvcolor{blue}

% font loading
% for luatex and xetex, do not use inputenc and fontenc
% see https://tex.stackexchange.com/a/496643
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

\usepackage[scale=0.90]{geometry}

\input{config.tex}
% \title{Resume}

\begin{document}
\hypersetup{pdftitle={Jason Huang - Resume}}

\makecvtitle


\vspace{-3em}

\section{Education}
\cventry{2021 -- 2025}{Computer Science Co-op}{McMaster University}{Hamilton, Ontario, Canada}{4.0 GPA}{
    Bachelor of Applied Science
    \begin{itemize}
        % \item{Received Faculty of Engineering Achievement Award for Fall 2021 term}
        \item Received
              Provost's Honour Roll (2021-2022),
              Deans' Honour List (2021-2024)
              % \item{Completed CS 2DB3: Databases - 4.0}
              % \item Completed CS 2C03: Data Structures and Algorithms - 4.0
              % \item Completed CS 2ME3: Intro to Software Development - 4.0
              % \item Completed CS 2GA3: Computer Architecture - 4.0
        \item Completed courses in
              Databases (4.0),
              Data Structures and Algorithms (4.0),
              Software Development (OOP and Design Patterns) (4.0),
              Information Security (4.0),
              Operating Systems (4.0),
              Introduction to Data Mining (4.0)
              Syntax-Based Tools and Compilers (4.0)
        \item{DeltaHacks Tech Exec, VP of Tech - (Nov 2022 -- Present)}
        \item{McMaster Competitive Programming ICPC Competitor (Spring 2023)}
    \end{itemize}
}

\section{Experience}
\cventry{Jun 2023 -- Present}{Founder, CTO}{SalesBop}{Hamilton, Ontario, Canada}{}{
    \url{https://www.salesbop.io}
    \begin{itemize}
        \item Architected a full-stack application for \textbf{LLM-driven sales call analysis} using \textbf{React and Python}, achieving an estimated \textbf{\$500k valuation}.
        \item Designed a \textbf{serverless, scalable infrastructure} with \textbf{Modal, Vercel, and PlanetScale}, integrating queues for reliable feedback generation.
        \item Built CI/CD pipelines with \textbf{GitHub Actions} and implemented security best practices, ensuring robust, secure, cost-efficient deployments.
        \item Mentored a co-founder on \textbf{React/JS development} and collaborated with stakeholders to define the product roadmap and prioritize features.
    \end{itemize}
}
\cventry{May 2024 -- Sept 2024}{Full Stack Developer}{Grapl}{Hamilton, Ontario, Canada}{}{
    \begin{itemize}
        \item Delivered a scalable full-stack inventory app with \textbf{React (Next.js)}, \textbf{PostgreSQL}, and \textbf{tRPC}, enhancing product functionality.
        \item Built a frame generation service using \textbf{Python} and \textbf{AWS Lambda}, boosting product capabilities.
        \item Streamlined deployment pipelines with \textbf{GitHub Actions} CI/CD and \textbf{Terraform}-based IaC, cutting deployment time by \textbf{50\%}.
    \end{itemize}
}
\cventry{May 2023 -- Sept 2023}{Cloud Engineering Intern}{Manulife}{Waterloo, Ontario, Canada}{}{
    \begin{itemize}
        \item Enhanced Terraform testing frameworks in \textbf{Go}, increasing test coverage by \textbf{25\%}.
        \item Scaffolded the ServiceNOW Terraform API in \textbf{Python}, enabling detailed cloud cost visibility.
        \item Collaborated with cross-functional teams using \textbf{Jira} and \textbf{Confluence} to deploy Kubernetes services via \textbf{Jenkins}.
    \end{itemize}
}
\cventry{May 2022 -- Sept 2022}{Software Engineer}{New Babel}{Toronto, Ontario, Canada}{}{
    \begin{itemize}
        \item Developed a high-performance API with \textbf{NoSQL}, serverless functions, and \textbf{Python}, ensuring rapid delivery.
        \item Collaborated in an \textbf{Agile} team to rapidly prototype features
        \item Presented technical solutions to \textbf{Fortune 500} clients, gathering feedback to iterate on product offerings.
    \end{itemize}
}
\cventry{Apr 2020 -- May 2022}{Software Architect}{TakingITGlobal}{Toronto, Ontario, Canada}{}{
    \begin{itemize}
        \item Released an accessibility toolkit as an open-source \textbf{NPM} module with a full \textbf{CI/CD} pipeline.
        \item Developed a scalable web application using \textbf{React} and \textbf{GraphQL}, streamlining grant administration for \textbf{400+ quarterly applicants}.
        \item Deployed a self-hosted CMS empowering a team of \textbf{30+ users} to manage content and dashboards effectively.
        \item Utilized \textbf{AWS}, \textbf{Netlify}, and \textbf{Auth0} to deploy and secure serverless applications.
    \end{itemize}
}

\section{Projects}
\cventry{Sept 2024 -- Present}{meetingbot}{}{}{}{
    \url{https://github.com/meetingbot/meetingbot}
    \begin{itemize}
        \item Developed an open-source platform to deploy meeting bots on private infrastructure using \textbf{Terraform}, \textbf{AWS APIs}, and \textbf{Python}, enhancing data privacy and reducing costs.
        \item Designed cost-efficient infrastructure with \textbf{scale-to-zero} functionality and seamless deployment using \textbf{Docker} and \textbf{Terraform}.
        \item Collaborated with a team of 6 to build a robust backend that integrates \textbf{NextJS}, \textbf{Puppeteer}, and multi-service support.
    \end{itemize}
}
\cventry{Nov 2022 -- Present}{DeltaHacks}{}{}{}{
    \url{https://github.com/deltahacks/portal} | \url{https://github.com/deltahacks/landing-11}
    \begin{itemize}
        \item Deployed a backend system for a shared applicant/administration portal, managing \textbf{over 1000 applicants}.
        \item Led a team of 4 to design and build a high-performance, responsive landing page using \textbf{AstroJS} and \textbf{React}.
    \end{itemize}
}
\cventry{Apr 2020 -- Present}{Homelab}{}{}{}{
    \begin{itemize}
        \item Deployed and managed \textbf{Docker} containers with \textbf{Docker Compose} on a hyperconverged server with \textbf{ZFS storage}.
        \item Experimented with \textbf{Kubernetes} (K3S) and Helm, implementing \textbf{Grafana} and \textbf{Prometheus} for system monitoring.
    \end{itemize}
}

% \section{Skills}
% \cvitem{Programming Languages}{C/C++, JavaScript, HTML/CSS, Python, Java, SQL (DB2, MySQL)}
% \cvitem{Tools \& Frameworks}{Linux, Git, Node.js, React, OpenAPI, Docker, Kubernetes, Terraform, GraphQL}
% \cvitem{Platforms \& Services}{GitHub, AWS, GCP, Azure, Vercel, PlanetScale, Jira / Confluence}
% \cvitem{Areas of Expertise}{Full-stack Web Development, Serverless Architecture, DevOps}

\end{document}