\documentclass[11pt, letterpaper, sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{black}

\usepackage{lipsum}

\usepackage[scale=0.75]{geometry}

\input{../../config.tex}
\title{Cover Letter}

% font loading
% for luatex and xetex, do not use inputenc and fontenc
% see https://tex.stackexchange.com/a/496643
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math} 
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

\begin{document}

\clearpage

\newcommand{\positionname}{Software Developer Co-op} % Position name
\newcommand{\companyname}{Nokia} % Company name

\recipient{HR Department}{\companyname{}} % Letter recipient
\date{\today} % Letter date
\opening{Dear Sir or Madam,} % Opening greeting
\closing{Sincerely yours,} % Closing phrase
\enclosure[Attached]{Résumé} % List of enclosed documents

\makelettertitle % Print letter title

I am pleased to be applying for the \positionname{} position at \companyname{}.
My experience with developing full-stack web applications,
with a focus on the back-end,
and my personal passion in computer infrastructure matches well with your requirements.
% TODO: ADD SOFT SKILLS THAT MATCH REQUIREMENTS
In addition, my background of working in small development teams
has taught me best practices in Agile,
and has provided me the skills necessary to thrive in a fast-paced environment.

At my previous position in New Babel,
I developed the company's flagship product, Pearl, a centralized database ID translation system.
I was responsible for the entire development process,
including research, design, implementation, and deployment.
I gained experience with AWS cloud architecture
and deployment automation tools such as Terraform,
and I used these skills to deploy a highly scalable multi-tenant SaaS REST API.
I also used AWS CodePipeline, moto, and pytest to fully automate the CI/CD process.

Furthermore, I have been working on a personal project, my homelab,
which is where I picked up my skills in Linux server administration,
networking, and cloud infrastructure.
Specifically, my experience in deploying a Cisco switch for my home network
introduced me to VLANs and network security,
which will be beneficial when working on the network tooling for this position.

% Ending paragraph
Thank you for taking the time to review my application.
I am passionate about the work your company does and would be honored to be a part of it.
I look forward to discussing this opportunity with you further,
and learning more about the position.

\makeletterclosing % Print letter signature

\newpage

\end{document}