\documentclass[11pt, letterpaper, sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{black}

\usepackage{lipsum}

\usepackage[scale=0.75]{geometry}

\input{../../config.tex}
\title{Cover Letter}

% font loading
% for luatex and xetex, do not use inputenc and fontenc
% see https://tex.stackexchange.com/a/496643
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math} 
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

\begin{document}

\clearpage

\newcommand{\positionname}{Controls Software Automation Engineering Internship} % Position name
\newcommand{\companyname}{Tesla} % Company name

\recipient{HR Department}{\companyname{}} % Letter recipient
\date{\today} % Letter date
\opening{Dear Sir or Madam,} % Opening greeting
\closing{Sincerely yours,} % Closing phrase
\enclosure[Attached]{Résumé} % List of enclosed documents

\makelettertitle % Print letter title

I am pleased to be applying for the \positionname{} position at \companyname{}.
My experience with in low-level programming,
algorithms,
and courses in computer architecture match the requirements of the position.
% TODO: ADD SOFT SKILLS THAT MATCH REQUIREMENTS
In addition, my background of working in small development teams
has taught me best practices in Agile,
and has provided me the skills necessary to thrive in a fast-paced environment.

At my previous position in New Babel,
I developed the company's flagship product, Pearl, a centralized database ID translation system.
I was responsible for the entire development process,
including research, design, implementation, and deployment.
While not directly related to the position,
the skills of innovating and building a product from the ground up,
in a limited timeframe transfers well to the demands of this position.

Furthermore, I have non-professional experience in hardware engineering,
from my time in my high school's robotics team.
As a lead engineer for our VEX robotics team,
I was responsible for designing and implementing
key mechanisms of the robot,
as well as introducing CAD modelling to our prototyping and design pipeline.

% Ending paragraph
Thank you for taking the time to review my application.
I am passionate about the work your company does and would be honored to be a part of it.
I look forward to discussing this opportunity with you further,
and learning more about the position.

\makeletterclosing % Print letter signature

\newpage

\end{document}