\documentclass[11pt, letterpaper, sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{black}

\usepackage{lipsum}

\usepackage[scale=0.75]{geometry}

\input{../../config.tex}
\title{Cover Letter}

% font loading
% for luatex and xetex, do not use inputenc and fontenc
% see https://tex.stackexchange.com/a/496643
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math} 
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

\begin{document}

\clearpage

\newcommand{\positionname}{Software Developer Intern} % Position name
\newcommand{\companyname}{D. E. Shaw Group} % Company name

\recipient{Hiring Manager}{\companyname{}} % Letter recipient
\date{\today} % Letter date
\opening{Dear Sir or Madam,} % Opening greeting
\closing{Sincerely,} % Closing phrase
\enclosure[Attached]{Resume} % List of enclosed documents

\makelettertitle % Print letter title

I am writing to apply for the Software Developer Intern position
in the Quantitative Strategies team at the D. E. Shaw group for Summer 2024.
As a Computer Science major at McMaster University,
I have consistently excelled in my coursework,
maintaining a 4.0 GPA and earning recognition for my academic excellence.

My technical acumen, honed through rigorous academic challenges and practical experiences,
aligns well with the dynamic environment at your firm.
In my previous internships, such as my role at Manulife,
I not only developed testing frameworks but also played a key role in enhancing global infrastructure visibility.
My project leadership at New Babel and efficiency improvements at TakingITGlobal showcase my ability to drive technical projects to success.

At the D. E. Shaw group, I am excited about the prospect
of applying my deep understanding of programming languages like
C/C++, JavaScript, Python, and tools such as React, Docker, Kubernetes, and Terraform.
I am particularly keen on utilizing these skills in developing tools for financial analysis and automated trading,
areas where I see significant scope for innovation and impact.

I look forward to the opportunity to discuss how my academic achievements and technical skills
would be beneficial to your team. Thank you for considering my application.

\makeletterclosing % Print letter signature

\newpage

\end{document}