\documentclass[11pt, letterpaper, sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{black}

\usepackage{lipsum}

\usepackage[scale=0.75]{geometry}

\input{../../config.tex}
\title{Cover Letter}

% font loading
% for luatex and xetex, do not use inputenc and fontenc
% see https://tex.stackexchange.com/a/496643
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math} 
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

\begin{document}

\clearpage

\newcommand{\positionname}{Software Developer Intern} % Position name
\newcommand{\companyname}{Konrad Group} % Company name

\recipient{Hiring Manager}{\companyname{}} % Letter recipient
\date{\today} % Letter date
\opening{Dear Sir or Madam,} % Opening greeting
\closing{Sincerely,} % Closing phrase
\enclosure[Attached]{Resume} % List of enclosed documents

\makelettertitle % Print letter title

I am writing to express my interest in the Software Developer Intern position at Konrad, as advertised.
Currently a Computer Science Co-op student at McMaster University with a 4.0 GPA,
my academic and professional experiences have equipped me with a solid foundation in both front end and back end development,
aligning perfectly with the requirements of this role.

During my internships at Manulife, New Babel, and TakingITGlobal,
I have honed my skills in various technologies including HTML/CSS/JavaScript, React, Docker, and Kubernetes.
My work has consistently contributed to significant improvements in project outcomes,
such as enhancing test coverage by over 25\% at Manulife
and increasing site performance by 800\% at TakingITGlobal.
My ability to work collaboratively in a team has been a key aspect of my success,
as demonstrated by my involvement in Agile development projects and my proactive communication in cross-functional teams.

I am particularly excited about the opportunity at Konrad because of the focus on both consumer and enterprise applications.
The role aligns with my passion for improving software development workflows/processes
and my commitment to writing maintainable, testable, and performant software.
Additionally, the prospect of working under a mentor
and being part of a world-class team is an ideal platform for me to both contribute to and learn from.

I am enthusiastic about the possibility of joining Konrad and believe that my technical skills,
combined with my strong interpersonal skills and proactive nature, make me a perfect fit for this position.
I look forward to the possibility of discussing my application with you in more detail.

Thank you for considering my application.
I am eager to bring my passion for software development to Konrad and contribute to the success of your team.

\makeletterclosing % Print letter signature

\newpage

\end{document}